### 2010-02-24 kivaSections.tex
I'm confused
wtf

%kkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkkk
\documentclass[12pt]{article}
\usepackage{graphicx,amssymb}

@@

In 2003, three different observers flew over the rivers. Assuming that no tracks 
are laid down between individuals’ flights on the same day, all three people 
should have seen the same tracks. While there is some error in classifying which 
site the observer saw the actual track in, each observer should at least be 
seeing the same, or nearly the same, number of sites with tracks. However, we 
did not find that to be the case. If we look only at days that all three people 
observed, there appear to be major differences among the proportion of sites in 
which the scientists detected a track (Figure x). The difference in estimated na
\"ive occupancy among the observers indicates that the scientists did not always 
correctly identify the tracks.

@@

Figure x caption:
The box plots show how the proportion of sites in which an observer saw tracks 
(“occupancy”) differs among the three observers. Only those dates in which all 
three observers flew are included.

@@

>>>>

pppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppppp
\documentclass[12pt]{article}
\usepackage{graphicx,amssymb}

@@

In 2003, three different observers flew over the rivers. Assuming that no tracks 
are laid down between individuals’ flights on the same day, all three people 
should have seen the same tracks. While there is some error in classifying which 
site the observer saw the actual track in, each observer should at least be 
seeing the same, or nearly the same, number of sites with tracks. However, we 
did not find that to be the case. If we look only at days that all three people 
observed, there appear to be major differences among the proportion of sites in 
which the scientists detected a track (Figure x). The difference in estimated 
na\"ive occupancy among the observers indicates that the scientists did not 
always correctly identify the tracks.

@@

@@

Figure x caption:
The box plots show how the proportion of sites in which an observer saw tracks 
(``occupancy") differs among the three observers. Only those dates in which all 
three observers flew are included.
